\textbf{Political Instability and Financial Markets}

### 2017-02-20 doc/paper.tex
Add Egypt plot to tex file
Sensitivity positive/negative CAR
Change to real returns

\begin{table}[!ht]
\caption{Abnormal returns following coups} \label{tab:AR-coups}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
  \hline
  \hline
\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
\cmidrule(r){3-5} \cmidrule(r){6-7}
\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
  \hline
\ExpandableInput{../tables/artable-coups-car.txt}
  \hline
  \textbf{Means} &  &  &  &  &  &  \\
\ExpandableInput{../tables/artable-coups-car-mean.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors are in parentheses. Statistical significance at the 10\%, 5\%, and 1\% level is denoted by *, ** and *** respectively. ``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level.
\end{threeparttable}
\end{center}
\end{table}

@@

\begin{figure}[htb]
\includegraphics{../figs/daily_mean_absreturn.pdf}
\caption{Mean of volatility estimates from GARCH(1,1) models}
\label{fig:volatility}
\end{figure}

@@

\begin{table}[!ht]
\caption{Non-parametric tests of the impact of regime changes} \label{tab:non-parametric}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}d{1.3}d{1.3}d{1.3}d{1.3}d{1.3}d{1.3}d{1.3}}
  \hline
  \hline
&\multicolumn{3}{c}{Regime Change Country}&\multicolumn{3}{c}{Synthetic Control Portfolio}&\multicolumn{1}{c}{\multirow{2}{*}{Wilcoxon}}\\
\cmidrule(r){2-4} \cmidrule(r){5-7}
&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{Sign}
&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{Sign}
&\multicolumn{1}{c}{Rank Test}\\
\multicolumn{1}{c}{Event Type}&\multicolumn{1}{c}{CAR (0,0)}&\multicolumn{1}{c}{p-value}&\multicolumn{1}{c}{p-value}
&\multicolumn{1}{c}{CAR (0,0)}&\multicolumn{1}{c}{p-value}&\multicolumn{1}{c}{p-value}
&\multicolumn{1}{c}{p-Value}\\
  \hline
Coups & -0.182 & 0.008 & 0.083 & 0.235 & 0.980 & 1.000 & 0.034  \\
Assassinations & -1.101 & 0.043 & 0.157 & -2.342 & 0.236 & 0.157 & 0.688  \\
Resignations & 6.146 & 0.000 & 0.020 & 0.486 & 0.217 & 0.796 & 0.007 \\
All (Absolute Value) & 3.725 & 0.000 & 0.004 & 0.335 & 0.144 & 0.612 & 0.001 \\
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes:
\end{threeparttable}
\end{center}
\end{table}

@@

\begin{figure}[!ht]
\includegraphics{../figs/daily_mean_absreturn.pdf}
\caption{Mean cumulative abnormal returns surrounding regime changes}
\label{fig:CAR-mean}
\end{figure}

@@

To check for the possibility that my previous results were spurious, a final placebo check examines whether there are abnormal absolute returns on the event day when the event day is shifted forward and backwards in time. Events are shifted backwards by 5, 10, 15, 20, 25 and 30 trading days and forwards by 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55 and 60 trading days.\footnote{Event days are not shifted backwards by more than 30 trading days to ensure than every country in the sample can be included. When events are shifted backwards by more than 30 trading days mean abnormal absolute returns continue to cluster around 0.} Figure~\autoref{fig:time-placebos} graphs the abnormal absolute returns (labeled CAR(0,0) in the figure) against the number of days shifted.

The largest CAR(0,0) occurs when the events have not been shifted in time. Moreover, the backwards shifted event day abnormal absolute return is only statistically different from zero when the event day is shifted backwards by 5 days. On the other hand, the forwards shifted CAR(0,0) is statistically significant when the event day is shifted forward by 5, 10, 15 and 20 days. These findings are consistent with figure~\autoref{fig:volatility}, in which volatility began increasing around 5 trading days before the event and then started decreasing quickly about 20 trading days therafter.

\begin{figure}[!ht]
\includegraphics{../figs/daily_mean_absreturn.pdf}
\vspace{-50pt}
\caption{Time-shifed placebos for absolute abnormal returns}
\label{fig:time-placebos}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics{../figs/daily_mean_absreturn.pdf}
\caption{Cumulative abnormal returns during the Egyptian revolution}
\label{fig:CAR-Egypt}
\end{figure}

>>>>

\begin{table}[!ht]
\caption{Abnormal returns following coups} \label{tab:AR-coups}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
  \hline
  \hline
\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
\cmidrule(r){3-5} \cmidrule(r){6-7}
\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
  \hline
\ExpandableInput{../tables/artable-coups-car.txt}
  \hline
\ExpandableInput{../tables/artable-coups-car-mean.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors are in parentheses. Statistical significance at the 10\%, 5\%, and 1\% level is denoted by *, ** and *** respectively. ``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level.
\end{threeparttable}
\end{center}
\end{table}

@@

\begin{figure}[htb]
\includegraphics{../figs/mean-volatility.pdf}
\caption{Mean of volatility estimates from GARCH(1,1) models}
\label{fig:volatility}
\end{figure}

@@

\begin{table}[!ht]
\caption{Non-parametric tests of the impact of regime changes} \label{tab:non-parametric}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}d{1.3}d{1.3}d{1.3}d{1.3}d{1.3}d{1.3}d{1.3}}
  \hline
  \hline
&\multicolumn{3}{c}{Regime Change Country}&\multicolumn{3}{c}{Synthetic Control Portfolio}&\multicolumn{1}{c}{\multirow{2}{*}{Wilcoxon}}\\
\cmidrule(r){2-4} \cmidrule(r){5-7}
&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{Sign}
&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{Sign}
&\multicolumn{1}{c}{Rank Test}\\
\multicolumn{1}{c}{Event Type}&\multicolumn{1}{c}{CAR (0,0)}&\multicolumn{1}{c}{p-value}&\multicolumn{1}{c}{p-value}
&\multicolumn{1}{c}{CAR (0,0)}&\multicolumn{1}{c}{p-value}&\multicolumn{1}{c}{p-value}
&\multicolumn{1}{c}{p-Value}\\
  \hline
\ExpandableInput{../tables/non-parametric-ar0.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Estimates for assassinations do not include the assassination of U.S. president William McKinley in 1901 because no control portfolios are available. 
\end{threeparttable}
\end{center}
\end{table}

@@

\begin{figure}[!ht]
\includegraphics{../figs/mean-car-pos-neg.pdf}
\caption{Mean cumulative abnormal returns surrounding regime changes}
\label{fig:CAR-mean}
\end{figure}

@@

Fianlly, to check whether our results are sensitive to model specificaiton, we estimated market models in addition to the baseline constant returns model. We used the MSCI World Index as a proxy for ther market return. [To do: add table for this]

@@

\begin{figure}[!ht]
\includegraphics{../figs/egypt-revolution-2011.pdf}
\caption{Cumulative abnormal returns during the Egyptian revolution}
\label{fig:CAR-Egypt}
\end{figure}
